---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# targetutils

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R build status](https://github.com/RHReynolds/rutils/workflows/R-CMD-check-bioc/badge.svg)](https://github.com/RHReynolds/rutils/actions)
[![Codecov test coverage](https://codecov.io/gh/RHReynolds/rutils/branch/master/graph/badge.svg)](https://codecov.io/gh/RHReynolds/rutils?branch=master)
[![Codecov test coverage](https://codecov.io/gh/RHReynolds/targetutils/branch/main/graph/badge.svg)](https://app.codecov.io/gh/RHReynolds/targetutils?branch=main)
<!-- badges: end -->

The goal of `targetutils` is to house common utility functions used in R targets pipelines. 

## Installation instructions

```{r "install_dev", eval = FALSE}
# you can install the development version of targetutils from GitHub:
# install.packages("devtools")
devtools::install_github("RHReynolds/targetutils")
```

## Citation

```{r citing-targetutils, eval = F}
citation("targetutils")
```

## Acknowledgements

* `targetutils` was developed using `r BiocStyle::Biocpkg("biocthis")`.

## Code of Conduct
Please note that the targetutils project is released with a [Contributor Code of Conduct](http://bioconductor.org/about/code-of-conduct/). By contributing to this project, you agree to abide by its terms.


